---
title: 'Reproducible Research: Peer Assessment 1'
output:
  pdf_document: default
  html_document:
    keep_md: yes
---


## Loading and preprocessing the data
```{r}
library(base)
step_data <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?
A histogram of the number of steps per day is given below, and 
using the following code:
```{r}
steps_5min <- step_data$steps[
    !is.na(step_data$steps)
]
day_factor <- as.factor(
    step_data$date[
        !is.na(step_data$steps)
    ]
)
steps_per_day <- tapply(steps_5min, day_factor, sum)
barplot(steps_per_day[!is.na(steps_per_day)])
```


The mean of the total number of steps per day is given here:
```{r}
mean(steps_per_day[!is.na(steps_per_day)])
```

The median is given below:
```{r}
median(steps_per_day[!is.na(steps_per_day)])
```


## What is the average daily activity pattern?

The following is the source code and plot for the number of steps
per five minute interval averaged over all days:
```{r}
intrvl_factor <- as.factor(
    step_data$interval[
        !is.na(step_data$steps)
    ]
)
steps_per_int <- tapply(steps_5min, intrvl_factor, mean)

plot(steps_per_int,
     type="l",
     ylab="Number of steps",
     xlab="5 minute interval"
   )
```

The maximum number of steps is located at 5 minute interval label 
given below:

```{r}
which.max(steps_per_int)[[1]]
```




## Imputing missing values

The number of missing values is given by:
```{r}
sum(is.na(step_data$steps))
```


All missing data will be imputed by substitution, 
at the appropriate interval value, of 
the number of steps per interval averaged over all days 
with the following code:
```{r}
step_data_noNA <- step_data
for(i in seq(1,length(steps_per_int))) {
    step_data_noNA[is.na(step_data$steps) 
               & 
               as.character(step_data_noNA$interval) 
                   == row.names(as.matrix(steps_per_int))[i]
              ,1] <- as.matrix(steps_per_int)[i]
}

sum(is.na(step_data_noNA$steps))
```

A histogram of the number of steps per day is given below, and 
using the following code:
```{r}
day_factor_noNA <- as.factor(step_data_noNA$date)
steps_per_day_noNA <- tapply(step_data_noNA$steps, day_factor_noNA, sum)
barplot(steps_per_day_noNA)
```


The mean of the total number of steps per day is given here:
```{r}
mean(steps_per_day_noNA)
```

The median is given below:
```{r}
median(steps_per_day_noNA)
```

Offhand, the differences do not appear to be significant.  


## Are there differences in activity patterns between weekdays and weekends?
